Programming Assignment 2

### 2015-04-02 paper.tex
Oh no theres a merge error on the paper

\subsection{Image Encoding}
the image encoding blah blah. Type here

@@

\subsection{Performance}
The Hamming/MAX did an excellent job when classifying animals. Both the aquatic classes and the planes had classifications that were completely incorrect, and another that was completely correct. We attribute this half-sided success to the images we selected for testing and for centroid-generation; the animals were distinct enough that we could tell the difference between the centroids when viewing them. The planes were a mess of lines due to poor image selection. The ships had very sporatic images used to train, and the resultant centroid was a mess. 
\subsection{Sensitivity}
This network was very sensitive to noise. Because it was feed-forward and used hamming distance between vectors, the most important thing was literally how many pixels matched up. Because of this, noise was very detrimental to classification accuracy.

\subsection{Comments}
We constructed out Hamming/MAX layer as per instructions of Lab 2. This led us to become extremely confused, as we weren't using a neural network but the linear-algebra equivalent. We didn't really use neurons. We just used applied linear algebra. Regardless, we went forward with the matrix-only implementation and were pretty pleased with the results.

By far the Hamming/Max was easiest for us to break down and implement.

@@

\subsubsection{Classifications}
The classifications used by BAM were encoded as orthogoal vectors of length 6.
Each class 'supersection' had a total of 3 classes. The animal supersection
includes Dogs, Elephants, and Giraffes. The Plane supersection includes Biplanes,
Jets, and Airbuses. Finally the Marine supersection includes Ships, Submarines,
and Whales. Each supersection is treated separately. The encodings for Animals
are used again in Planes and Marines. This was to make the classification
encodings as simple yet distant as possible.
\subsection{Performance}
The Bidirectional Associative Memory implementation performed rather poorly.
Most of the associations were directed towards a specific centroid, resulting
in at least 1 'class' performing extremely well. The results of our
experiment are as follows.
Animal Results:
    Dog:
        7 Correctly Classified
        3 Incorrectly Classified
    Elephant:
        1 Correctly Classified
        9 Incorrectly Classified
    Giraffe:
        0 Correctly Classified
        9 Correctly Classifed
Plane Results:
    Biplane:
        0 Correctly Classified
        10 Incorrectly Classified
    Jet Results:
        5 Correctly Classified
        5 Incorrectly Classified
    Airbus Results:
        0 Correctly Classified
        7 Incorrectly Classified
Marine Results:
    Ships:
        0 Correctly Classified
        5 Incorrectly Classified
    Submarine Results:
        8 Correctly Classified
        0 Incorrectly Classified
    Whale Results:
        3 Correctly Classified
        7 Incorrectly Classified

@@

@@

\subsection{Performance}
Our LVQ had some pretty good performance but also some poor performance.  When testing animals against eachother (dogs, elephants, and giraffes) the network maintained a fairly consistent classification.  It returned 21\% false negatives by misclassifying 4 dogs and 2 elephants, all as giraffes.  However the other 79\% of animals were correctly classified.  Aircraft were a little trickier.  With 66\% overall correct classification, most aircraft were classified as Jetfighters. All ten jet fighters were correctly classified and 9 passenger aircraft and biplanes misclassified.  Sea-fareing objects were not as great.  Not a single image was classified as a ship.  However, 70\% of whales were correctly classified and all of the submarines were correctly classified.
\begin{itemize}
\end{itemize}

>>>>

\subsection{Image Encoding}
The image encoding... blah blah. Type here

@@

@@

\subsubsection{Classifications}
The classifications used by BAM were encoded as orthogoal vectors of length 6.
Each class 'supersection' had a total of 3 classes. The animal supersection
includes Dogs, Elephants, and Giraffes. The Plane supersection includes Biplanes,
Jets, and Airbuses. Finally the Marine supersection includes Ships, Submarines,
and Whales. Each supersection is treated separately. The encodings for Animals
are used again in Planes and Marines. This was to make the classification
encodings as simple yet distant as possible.

\subsection{Performance}
The Bidirectional Associative Memory implementation performed rather poorly.
Most of the associations were directed towards a specific centroid, resulting
in at least 1 'class' performing extremely well. The results of our
experiment are as follows.
Animal Results:
    Dog:
        7 Correctly Classified
        3 Incorrectly Classified
    Elephant:
        1 Correctly Classified
        9 Incorrectly Classified
    Giraffe:
        0 Correctly Classified
        9 Correctly Classifed
Plane Results:
    Biplane:
        0 Correctly Classified
        10 Incorrectly Classified
    Jet Results:
        5 Correctly Classified
        5 Incorrectly Classified
    Airbus Results:
        0 Correctly Classified
        7 Incorrectly Classified
Marine Results:
    Ships:
        0 Correctly Classified
        5 Incorrectly Classified
    Submarine Results:
        8 Correctly Classified
        0 Incorrectly Classified
    Whale Results:
        3 Correctly Classified
        7 Incorrectly Classified

@@

These errors are likely due to bad encoding. Our group noticed that large
images with thin outlines lost information when being resized to a smaller 
image. Also most of our outlines were collected from the internet. These
outlines were incredibly diverse and perhaps the details of each image were
simply 'drowned' out in the diversity of the images. If we standardized our 
input we would have likely seen better results.

@@
